\newpage
\begin{thebibliography}{9}
\addcontentsline{toc}{section}{Βιβλιογραφία}
%\bibliographystyle{plain}
%\bibliography{\jobname}
\bibitem{Improper Neutralization of Script in Attributes in a Web Page} 
Improper Neutralization of Script in Attributes in a Web Page. [\textit{CWE-83}],  \\ \url{https://cwe.mitre.org/data/definitions/83.html}

\bibitem{Cross-site scripting (XSS) vulnerability in SCT Campus Pipeline allows remote attackers to inject arbitrary web script or HTML via onload, onmouseover, and other Javascript events in an e-mail attachment.} 
Cross-site scripting (XSS) vulnerability in SCT Campus Pipeline allows remote attackers to inject arbitrary web script or HTML via onload, onmouseover, and other Javascript events in an e-mail attachment.  [\textit{CVE-2004-1935}],  \\ \url{https://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2004-1935}

\bibitem{Cross-site scripting (XSS) vulnerability in ACS Blog 1.1.1 allows remote attackers to inject arbitrary web script or HTML via onmouseover or onload events in (1) img, (2) link, or (3) mail tags. } 
Cross-site scripting (XSS) vulnerability in ACS Blog 1.1.1 allows remote attackers to inject arbitrary web script or HTML via onmouseover or onload events in (1) img, (2) link, or (3) mail tags.  [\textit{CVE-2005-0945}],  \\ \url{https://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2005-0945}

\bibitem{SCT Campus Pipeline email attachments could allow cross-site scripting} 
SCT Campus Pipeline email attachments could allow cross-site scripting.  \textit{IBMCloud} [\textit{CVE-2004-1935}], Apr 15 2004  \\ \url{https://exchange.xforce.ibmcloud.com/vulnerabilities/15878}

\bibitem{ SCT Campus Pipeline Email Attachment Script Injection Vulnerability} 
 SCT Campus Pipeline Email Attachment Script Injection Vulnerability. \textit{SecurityFocus}, [\textit{CVE-2004-1935}], Apr 15 2004 \\ \url{https://www.securityfocus.com/bid/10154}
 
\bibitem{CVSS Scores & Vulnerability Types} 
 	CVSS Scores \& Vulnerability Types. \textit{CVE Details}, [\textit{CVE-2004-1935}], Apr 15 2004  \\ \url{https://www.cvedetails.com/cve/CVE-2004-1935/?q=CVE-2004-1935}

\bibitem{SCT javascript execution vulnerability} 
SCT javascript execution vulnerability. \textit{Marc.info}, [\textit{CVE-2004-1935}],  \\ \url{https://marc.info/?l=bugtraq&m=108207280917231&w=2}

%%

\bibitem{Multiple XSS vulnerabilities in ACS Blog} 
Multiple XSS vulnerabilities in ACS Blog. \textit{Marc.info}, [\textit{CVE-2005-0945}],  Mar 28 2005 \\ \url{https://marc.info/?l=bugtraq&m=111214069029812&w=2}

\bibitem{CVSS Scores & Vulnerability Types } 
CVSS Scores \& Vulnerability Types . \textit{CVE Details} [\textit{CVE-2005-0945}], May 2 2005   \\ \url{https://www.cvedetails.com/cve/CVE-2005-0945/}

\bibitem{ ACS Blog Name Field HTML Injection Vulnerability} 
 ACS Blog Name Field HTML Injection Vulnerability. \textit{SecurityFocus}, [\textit{CVE-2005-0945}], Mar 28 2005  \\ \url{https://www.securityfocus.com/bid/12921/info}
 
\bibitem{ CVE-2005-0945 Detail } 
 CVE-2005-0945 Detail . \textit{NIST}, [\textit{CVE-2005-0945}], May 2 2005 \\ \url{https://nvd.nist.gov/vuln/detail/CVE-2005-0945}

\bibitem{ ACS Blog link, mail, and img tags cross-site scripting } 
 ACS Blog link, mail, and img tags cross-site scripting . \textit{IBMCloud}, [\textit{CVE-2005-0945}],  Mar 28 2005 \\ \url{https://exchange.xforce.ibmcloud.com/vulnerabilities/19864}

\bibitem{ ACS Blog Input Validation Errors in 'Comments' Tags Let Remote Users Conduct Cross-Site Scripting Attacks} 
 ACS Blog Input Validation Errors in 'Comments' Tags Let Remote Users Conduct Cross-Site Scripting Attacks . \textit{SecurityTracker}, [\textit{CVE-2005-0945}],  Mar 28 2005  \\ \url{https://securitytracker.com/id?1013584}



%%

\bibitem{xss-filter-evasion} 
Jim Manico, Abdullah Hussam, Michael McCabe, Luke Plant, Randomm, David Shaw, ALange, Matt Tesauro, Adam Caudill, Anandu, DhirajMishra, Ono, Bill Sempf, Dan Wallis, Peter Mosmans, Dominique Righetto. (\textit{OWASP}) [\textit{XSS Filter Evasion Cheat Sheet}],\\ \url{https://owasp.org/www-community/xss-filter-evasion-cheatsheet}{\color{black}}

\bibitem{Cross Site Scripting (XSS)} 
KirstenS, Jim Manico, Jeff Williams, Dave Wichers, Adar Weidman, Roman, Alan Jex, Andrew Smith, Jeff Knutson, Imifos, Erez Yalon. (\textit{OWASP}) [\textit{Cross Site Scripting (XSS)}],\\ \url{https://owasp.org/www-community/attacks/xss/}{\color{black}}

\bibitem{Types of XSS} 
OWASP: Types of XSS,\\ \url{https://owasp.org/www-community/Types_of_Cross-Site_Scripting}{\color{black}}

\bibitem{DOM based XSS Prevention Cheat Sheet} 
OWASP: DOM based XSS Prevention Cheat Sheet,\\ \url{https://cheatsheetseries.owasp.org/cheatsheets/DOM_based_XSS_Prevention_Cheat_Sheet.html}{\color{black}}

\bibitem{Cross-Site Scripting (XSS) Attack Lab} 
Jim Wenliang Du, \textit{Syracuse University}. (\textit{SEED Labs}) [\textit{Cross-Site Scripting (XSS) Attack Lab}], 2006-2016, \\ \url{https://seedsecuritylabs.org/Labs_16.04/PDF/Web_XSS_Elgg.pdf}{\color{black}}

\bibitem{Ασφάλεια υπολογιστών - Αρχές και πρακτικές} 
WILLIAM STALLINGS and LAWRIE BROWN. 
\textit{[Ασφάλεια υπολογιστών - Αρχές και πρακτικές]}. 3η αμερικάνικη εκδοσή, 
\textit{ΕΚΔΟΣΕΙΣ ΚΛΕΙΔΑΡΙΘΜΟΣ ΕΠΕ}.

\bibitem{Κρυπτογραφία και Ασφάλεια Δικτύων Αρχές και Εφαρμογές} 
Stallings William. 
\textit{[Κρυπτογραφία και Ασφάλεια Δικτύων Αρχές και Εφαρμογές]}. 
\textit{Εκδοτικός Όμιλος ΙΩΝ}.

\end{thebibliography}